Lab News

### 2023-09-06 index.qmd
update with new paper acceptance

@@

<font color="#d08770">[May 26 2023].</font> **Paper accepted**. Lokesh, R., Sullivan, S.R., St. Germain, L., Roth, A.M., Calalo, J.A., Buggeln, J., Ngo, T., Marchhart, V.R.F., Carter, M.J, & Cashaback, J.G.A. Visual accuracy dominates over haptic speed for state estimation of a partner during collaborative sensorimotor interactions. *Journal of Neurophysiology*.

>>>>

<font color="#d08770">[May 26 2023].</font> **Paper accepted**.   Roth, A.M., Calalo, J.A., Lokesh, R., Sullivan, S.R., Grill, S., Jeka, J.J., van der Kooij, K., Carter, M.J, & Cashaback, J.G.A. Reinforcement-based processes actively regulate motor exploration along redundant solution manifolds. *Proceedings of the Royal Society B*.

@@
